

<http://shiny.rstudio.com/tutorial/lesson3/>
<http://shiny.rstudio.com/gallery/widget-gallery.html>
<http://shiny.rstudio.com/articles/shinyapps.html>
**some prerequisites**
Shiny doesn't really require it, but as with all web programming, a little knowledge of html, css
and js is very helpful
There are too many tutorials online to count for getting basic proficiency in these topics to count.
Shiny uses bootstrap (no relation to the statistics bootstrap) style, which (to me) seems to look
nice and renders well on mobile platforms
·
html gives a web page structure and sectioning as well as markup instructions
css gives the style
js for interactivity

**what else is out there?**
.Creating any solution requiring fairly deep knowledge of web client/server programming
.OpenCPU by Jerome Ooms, is a really neat project providing an API for calling R from web
documents

- And he even hosts an OpenCPU server, but you can create your own


let's make this prediction
```{r}
diabetesRisk <- function(glucose) glucose/200
```


**Getting started**
.Make sure you have the latest release of R installed
.If on windows, make sure that you have Rtools installed
```{r}
#install.packages("shiny")
#libray(shiny)
```


.Great tutorial at <http://rstudio.github.io/shiny/tutorial/>
.Basically, this lecture is walking through that tutorial offering some of our insights
.Note, some of the proposed interactive plotting uses of Shiny could be handled by the very
simple manipulate function rstudio manipulate
.Also, rCharts is will be covered in a different lecture.


**A shiny project**
A shiny project is a directory containing at least two parts
.One named ui.R (for user interface) controls how it looks.
.One named server.R that controls what it does.


**ui.R**
```{r}
library(shiny)
shinyUI(pageWithSidebar(
 headerPanel("Data science FTW!"),
 sidebarPanel(
 h3('Sidebar text')
 ),
 mainPanel(
 h3('Main Panel text')
 )
))

#h3 means the third level html heading
```


**server.R**
```{r}
library(shiny)
shinyServer(
 function(input, output) {
 }
)
```



**To run it**

In R, change to the directories with these files and type runApp()
.or put the path to the directory as an argument
.It should open an browser window with the app running




**R functions for html markup**
ui.R
```{r}

shinyUI(pageWithSidebar(
 headerPanel("Illustrating markup"),
 sidebarPanel(
 h1('Sidebar panel'),
 h1('H1 text'),
 h2('H2 Text'),
 h3('H3 Text'),
 h4('H4 Text')
 ),
 mainPanel(
 h3('Main Panel text'),
 code('some code'),
 p('some ordinary text')
 )
))
```



**illustrating inputs ui.R**
```{r}
shinyUI(pageWithSidebar(
 headerPanel("Illustrating inputs"),
 sidebarPanel(
 numericInput('id1', 'Numeric input, labeled id1', 0, min = 0, max = 10, step = 1),
 checkboxGroupInput("id2", "Checkbox",
 c("Value 1" = "1",
 "Value 2" = "2",
 "Value 3" = "3")),
 dateInput("date", "Date:")
 ),
 mainPanel(
 )
))
```



**Part of ui.R**
```{r}
 mainPanel(
 h3('Illustrating outputs'),
 h4('You entered'),
 verbatimTextOutput("oid1"),
 h4('You entered'),
 verbatimTextOutput("oid2"),
 h4('You entered'),
 verbatimTextOutput("odate")
 )
```


 h4('You entered'),
 

**server.R**
```{r}
shinyServer(
 function(input, output) {
 output$oid1 <- renderPrint({input$id1})
 output$oid2 <- renderPrint({input$id2})
 output$odate <- renderPrint({input$date})
 }
)
```



**Let's build our prediction function**
 1) ui.R
```{r}
shinyUI(
 pageWithSidebar(
 # Application title
 headerPanel("Diabetes prediction"),
 sidebarPanel(
 numericInput('glucose', 'Glucose mg/dl', 90, min = 50, max = 200, step = 5),
 submitButton('Submit')
 ),
 mainPanel(
 h3('Results of prediction'),
 h4('You entered'),
 verbatimTextOutput("inputValue"),
 h4('Which resulted in a prediction of '),
 verbatimTextOutput("prediction")
 )
 )
)f
```


2) server.R
```{r}
diabetesRisk <- function(glucose) glucose / 200
shinyServer(
 function(input, output) {
 output$inputValue <- renderPrint({input$glucose})
 output$prediction <- renderPrint({diabetesRisk(input$glucose)})
 }
)
```


****Shiny 2***
**Details**

Code that you put before shinyServer in the server.R function gets called once when you do runApp()
Code inside the unnamed function of shinyServer(function(input, output){ but not in a reactive statement will run once for every new user (or page refresh)
Code in reactive functions of shinyServer get run repeatedly as needed when new values are entered (reactive functions are those like render*)


**Experiment (code in the slidify document)**
ui.R
```{r}
shinyUI(pageWithSidebar(
  headerPanel("Hello Shiny!"),
  sidebarPanel(
      textInput(inputId="text1", label = "Input Text1"),
      textInput(inputId="text2", label = "Input Text2")
  ),
  mainPanel(
      p('Output text1'),
      textOutput('text1'),
      p('Output text2'),
      textOutput('text2'),
      p('Output text3'),
      textOutput('text3'),
      p('Outside text'),
      textOutput('text4'),
      p('Inside text, but non-reactive'),
      textOutput('text5')
  )
))
```


**Reactive expressions*

Sometimes to speed up your app, you want reactive operations (those operations that depend on widget input values) to be performed outside of a render*1 statement
For example, you want to do some code that gets reused in several render* statements and don't want to recalculate it for each
The reactive function is made for this purpose

.Example

server.R
```{r}
shinyServer(
  function(input, output) {
    x <- reactive({as.numeric(input$text1)+100})      
    output$text1 <- renderText({x()                          })
    output$text2 <- renderText({x() + as.numeric(input$text2)})
  }
)
```



**As opposed to**

```{r}
shinyServer(
  function(input, output) {
    output$text1 <- renderText({as.numeric(input$text1)+100  })
    output$text2 <- renderText({as.numeric(input$text1)+100 + 
        as.numeric(input$text2)})
  }
)
```



**Non-reactive reactivity (what?)**

Sometimes you don't want shiny to immediately perform reactive calculations from widget inputs
In other words, you want something like a submit button

ui.R
```{r}
shinyUI(pageWithSidebar(
  headerPanel("Hello Shiny!"),
  sidebarPanel(
      textInput(inputId="text1", label = "Input Text1"),
      textInput(inputId="text2", label = "Input Text2"),
      actionButton("goButton", "Go!")
  ),
  mainPanel(
      p('Output text1'),
      textOutput('text1'),
      p('Output text2'),
      textOutput('text2'),
      p('Output text3'),
      textOutput('text3')
  )
))
```


server.R
```{r}
shinyServer(
  function(input, output) {
    output$text1 <- renderText({input$text1})
    output$text2 <- renderText({input$text2})
    output$text3 <- renderText({
        input$goButton # create a depedency on the go button
        isolate(paste(input$text1, input$text2))
    })
  }
)
```



#Manipulate

Suppose that you want to create a quick interactive graphic
You have to do it now
The intended users also use Rstudio
manipulate is a really cool solution that is often all you need to quickly make interactive graphics
Documentation

Manipulate is well documented at the Rstudio web site here
<http://www.rstudio.com/ide/docs/advanced/manipulate>
From there, try this

```{r}
library(manipulate)
manipulate(plot(1:x), x = slider(1, 100))
```


You can create a slider, checkbox, or picker (drop down) and have more than one



**Example from the regression class**
```{r}

library(manipulate)
myHist <- function(mu){
  hist(galton$child,col="blue",breaks=100)
  lines(c(mu, mu), c(0, 150),col="red",lwd=5)
  mse <- mean((galton$child - mu)^2)
  text(63, 150, paste("mu = ", mu))
  text(63, 140, paste("MSE = ", round(mse, 2)))
}
manipulate(myHist(mu), mu = slider(62, 74, step = 0.5))
```


#rCharts
<http://ramnathv.github.io/rCharts/>
```{r}
require(slidify)
require(rCharts)
      haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)

n1$save('fig/n1.html', cdn = TRUE)
cat('<iframe src="fig/n1.html" width=100%, height=600></iframe>')

```

**Deconstructing another example**
```{r}
## Example 1 Facetted Scatterplot
names(iris) = gsub("\\.", "", names(iris))
r1 <- rPlot(SepalLength ~ SepalWidth | Species, data = iris, color = 'Species', type = 'point')
r1$save('fig/r1.html', cdn = TRUE)
cat('<iframe src="fig/r1.html" width=100%, height=600></iframe>')
```


**Example 2 Facetted Barplot**
```{r}
hair_eye = as.data.frame(HairEyeColor)
r2 <- rPlot(Freq ~ Hair | Eye, color = 'Eye', data = hair_eye, type = 'bar')
r2$save('fig/r2.html', cdn = TRUE)
cat('<iframe src="fig/r2.html" width=100%, height=600></iframe>')
```


**How to get the js/html or publish an rChart**
Now you can add whatever you'd like

```{r}

r1 <- rPlot(mpg ~ wt | am + vs, data = mtcars, type = "point", color = "gear")
r1$print("chart1") # print out the js 
r1$save('myPlot.html') #save as html file
r1$publish('myPlot', host = 'gist') # save to gist, rjson required
r1$publish('myPlot', host = 'rpubs') # save to rpubs
```

**morris**
```{r}
data(economics, package = "ggplot2")
econ <- transform(economics, date = as.character(date))
m1 <- mPlot(x = "date", y = c("psavert", "uempmed"), type = "Line", data = econ)
m1$set(pointSize = 0, lineWidth = 1)
m1$save('fig/m1.html', cdn = TRUE)
cat('<iframe src="fig/m1.html" width=100%, height=600></iframe>')
```


**xCharts**
```{r}
require(reshape2)
uspexp <- melt(USPersonalExpenditure)
names(uspexp)[1:2] = c("category", "year")
x1 <- xPlot(value ~ year, group = "category", data = uspexp, type = "line-dotted")
x1$save('fig/x1.html', cdn = TRUE)
cat('<iframe src="fig/x1.html" width=100%, height=600></iframe>')
```


**Leaflet**
```{r}
map3 <- Leaflet$new()
map3$setView(c(51.505, -0.09), zoom = 13)
map3$marker(c(51.5, -0.09), bindPopup = "<p> Hi. I am a popup </p>")
map3$marker(c(51.495, -0.083), bindPopup = "<p> Hi. I am another popup </p>")
map3$save('fig/map3.html', cdn = TRUE)
cat('<iframe src="fig/map3.html" width=100%, height=600></iframe>')
```


**Rickshaw**
```{r}
usp = reshape2::melt(USPersonalExpenditure)
# get the decades into a date Rickshaw likes
usp$Var2 <- as.numeric(as.POSIXct(paste0(usp$Var2, "-01-01")))
p4 <- Rickshaw$new()
p4$layer(value ~ Var2, group = "Var1", data = usp, type = "area", width = 560)
# add a helpful slider this easily; other features TRUE as a default
p4$set(slider = TRUE)
p4$save('fig/p4.html', cdn = TRUE)
cat('<iframe src="fig/p4.html" width=100%, height=600></iframe>')
```


**highchart**
```{r}
h1 <- hPlot(x = "Wr.Hnd", y = "NW.Hnd", data = MASS::survey, type = c("line", 
    "bubble", "scatter"), group = "Clap", size = "Age")
h1$save('fig/h1.html', cdn = TRUE)
cat('<iframe src="fig/h1.html" width=100%, height=600></iframe>')
```


rCharts summarized

rCharts makes creating interactive javascript visualizations in R ridiculously easy
However, non-trivial customization is going to require knowledge of javascript
If what you want is not too big of a deviation from the rCharts examples, then it's awesome
Otherwise, it's challenging to extend without fairly deep knowledge of the JS libraries that it's calling.
rCharts is under fairly rapid development



#plotly
```{r}
library("devtools")
install_github("ropensci/plotly")

#Plotly's R package is updated frequently! To upgrade, just re-install:

devtools::install_github("ropensci/plotly")

library(plotly)
set_credentials_file("eckameni", "3k0dxfzkoh")

```


**Start plotting!**
Make a plot with ggplot2, as usual:
```{r}
library(ggplot2)
data(iris)
ggiris <- qplot(Petal.Width, Sepal.Length, data = iris, color = Species)
ggiris
#Now make this plot interactive and online. To do this, first instantiate a Plotly object:

py <- plotly()
#And call the ggplotly() method to convert your ggplot2 plot into a Plotly plot:

r <- py$ggplotly(ggiris)
#Your online, interactive, collaborative plot lives at this URL:

r$response$url
```



example
```{r}
load("courseraData.rda")
```

