---
title       : loan calulator
subtitle    : financial plan
author      : ec
job         : student
logo        : Earth.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [bootstrap, quiz, mathjax, shiny, interactive]
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
---

<http://slidify.github.io/dcmeetup/demos/interactive/>

--- &radio
## Quiz
###Question 1

What is 1 + 1?

1. 1
2. _2_
3. 3
4. 4

*** .hint
This is a hint

*** .explanation
This is an explanation

--- &radio
## Quiz
###Question 2
What is 1 * 1?

1. _1_
2. 2
3. 3
4. 4

*** .hint
This is a hint

*** .explanation
This is an explanation

---

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- 

## Slide 2

You can include $\LaTeX$ math formatting as follows
Edit your YAML
widgets     : [mathjax]
Enter inline math code with `$x^2$` $x^2$
Enter centered code with 
`$$\frac{-b \pm \sqrt{b^2 - 4 a c}}{2a}$$` $$\frac{-b \pm \sqrt{b^2 - 4 a c}}{2a}$$

---
## Interactive Chart

```{r echo = F, results = 'asis'}
require(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)
n1$print('chart1')
```

--- &interactive
## Interactive Console

```{r opts.label = 'interactive', results = 'asis'}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
print(M1, tag = 'chart')
```


---
#Interactive Chart with Controls

```{r opts.label = 'shiny'}
slidifyUI(
  sidebarPanel(
    selectInput('sex', 'Choose Sex', c('Male', 'Female')),
    selectInput('type', 'Choose Type',
      c('multiBarChart', 'multiBarHorizontalChart')
    )
  ),
  mainPanel(
    tags$div(id = 'nvd3plot', class='shiny-html-output nvd3 rChart')
  )
)
```

